### 2018-03-16 submission/manuscript.Rmd
update first bray-curtis section results

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
Overall, there were a few sub-sampling dependent differences in bacterial communities between cycle number . First, independent of HiFi DNA polymerase there were differences for the same fecal sample between 20 versus 25 cycles that was dependent on sub-sampling depth (sub-sampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (25% - 75% quantile)), sub-sampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), sub-sampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A]. Second, where data is available for the mock communities, there were larger difference between 20 and 25 cycles (sub-sampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3B]. Third, using PERMANOVA to test for differences within HiFi DNA polymerase groups based on cycle number, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depth (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`, respectively). Phusion was one of only two HiFi DNA polymerases that that had fecal samples for the 1000 sub-sampling depth at 15 cycles. These stated differences between the next 5-cycle increment do not persist once 25 cycles are reached [Figure 3].

>>>>

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
A few small differences based on sub-sampling and cycle number were detected in bacterial communities. Within the same fecal sample and independent of HiFi DNA polymerases, there were differences in the community composition between 20 and 25 cycles that was dependent on sub-sampling depth (sub-sampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (25% - 75% quantile)), sub-sampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), sub-sampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A]. Further, where data was available for the mock communities, there were larger observed differences between 20 and 25 cycles (sub-sampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3B]. Additionally, these stated community differences disappear when comparing 25 to 30 cycles and do not persist past 25 cycles [Figure 3]. Finally, using PERMANOVA to test for community differences based on cycle number within HiFi DNA polymerases, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depths (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`, respectively). Phusion was one of two HiFi DNA polymerases that had enough sequences to reach a sub-sampling depth of 1000 at 15 cycles for fecal samples.

### 2018-03-16 submission/manuscript.tex
update first bray-curtis section results

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} Overall, there were a few sub-sampling dependent differences
in bacterial communities between cycle number . First, independent of
HiFi DNA polymerase there were differences for the same fecal sample
between 20 versus 25 cycles that was dependent on sub-sampling depth
(sub-sampled to 1000 = 0.51 (0.4 - 0.79) (median (25\% - 75\%
quantile)), sub-sampled to 5000 = 0.43 (0.33 - 0.63), sub-sampled to
10000 = 0.4 (0.24 - 0.43)) {[}Figure 3A{]}. Second, where data is
available for the mock communities, there were larger difference between
20 and 25 cycles (sub-sampled to 1000 = 0.88 (0.42 - 0.91)) {[}Figure
3B{]}. Third, using PERMANOVA to test for differences within HiFi DNA
polymerase groups based on cycle number, only Phusion had cycle
dependent differences at 1000 and 5000 sub-sampling depth (P-value =
0.03 and 0.01, respectively). Phusion was one of only two HiFi DNA
polymerases that that had fecal samples for the 1000 sub-sampling depth
at 15 cycles. These stated differences between the next 5-cycle
increment do not persist once 25 cycles are reached {[}Figure 3{]}.

>>>>

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} A few small differences based on sub-sampling and cycle number
were detected in bacterial communities. Within the same fecal sample and
independent of HiFi DNA polymerases, there were differences in the
community composition between 20 and 25 cycles that was dependent on
sub-sampling depth (sub-sampled to 1000 = 0.51 (0.4 - 0.79) (median
(25\% - 75\% quantile)), sub-sampled to 5000 = 0.43 (0.33 - 0.63),
sub-sampled to 10000 = 0.4 (0.24 - 0.43)) {[}Figure 3A{]}. Further,
where data was available for the mock communities, there were larger
observed differences between 20 and 25 cycles (sub-sampled to 1000 =
0.88 (0.42 - 0.91)) {[}Figure 3B{]}. Additionally, these stated
community differences disappear when comparing 25 to 30 cycles and do
not persist past 25 cycles {[}Figure 3{]}. Finally, using PERMANOVA to
test for community differences based on cycle number within HiFi DNA
polymerases, only Phusion had cycle dependent differences at 1000 and
5000 sub-sampling depths (P-value = 0.03 and 0.01, respectively).
Phusion was one of two HiFi DNA polymerases that had enough sequences to
reach a sub-sampling depth of 1000 at 15 cycles for fecal samples.
